\begin{thebibliography}{1}

\bibitem{1}
Matei Zaharia et al. Resilient distributed datasets: A fault-tolerant abstraction for in-memory cluster computing. In NSDI, 2012.


\bibitem{2}
Yucheng Low et al. Distributed GraphLab: A Framework for Machine Learning and Data Mining in the Cloud. PVLDB, 2012.

\bibitem{3}
Mu Li et al. Scaling distributed machine learning with the parameter server. In OSDI, 2014.

\bibitem{4} 
Ashish Thusoo et al. Data warehousing and analytics infrastructure at Facebook. SIGMOD, 2010.

\bibitem{5}
George Lee et al. The unified logging infrastructure for data analytics at Twitter. PVLDB, 2012.

\bibitem{6}
Aditya Auradkar et al. Data infrastructure at linkedIn. In ICDE, 2012.

\bibitem{7}
Ariel Rabkin et al. Aggregation and degradation in jetstream: Streaming analytics in the wide area. In NSDI, 2014.

\bibitem{8}
Ashish Vulimiri et al. Global analytics in the face of bandwidth and regulatory constraints. In NSDI, 2015.

\bibitem{9}
Nikolaos Laoutaris et al. Inter-datacenter bulk transfers with netstitcher. In SIGCOMM, 2011.

\bibitem{10}
Albert Greenberg et al. The cost of a cloud: research problems in data center networks. SIGCOMM, 2008.

\bibitem{11}
Martin Rost and Kirsten Bock. Privacy by design and the new protection goals. DuD, January, 2011.

\bibitem{12}
European Commission press release. Commission to pursue role as honest broker in future global negotiations on internet governance. \url{http: //europa.eu/rapid/press-release IP-14-142 en.htm}.

\bibitem{13}
Principal component analysis: \url{https://en.wikipedia.org/wiki/Principal_component_analysis}.

\bibitem{14}
J. Shlens. A tutorial on principal component analysis. \textit{arXiv preprint
arXiv:1404.1100}. 2014.

\bibitem{elgamal}
T. Elgamal and M. Hefeeda. Analysis of pca algorithms in distributed environments. \textit{arXiv preprint arXiv:1503.05214}. 2015.

\bibitem{16}
N. P. Halko. Randomized methods for computing low-rank approx- imations of matrices. Ph.D. dissertation, Boulder, CO, USA, 2012, aAI3507998.

\bibitem{17}
M. E. Tipping and C. M. Bishop. Probabilistic principal component analysis. \textit{Journal of the Royal Statistical Society: Series B (Statistical Methodology), vol. 61, no. 3, pp. 611?622}. 1999.

\bibitem{18}
S. Roweis. Em algorithms for pca and spca. \textit{Advances in neural information processing systems, pp. 626?632} 1998.

\bibitem{pca}
I. Jolliffe. Principal component analysis. 1986. 1986.

\bibitem{kraska}
T. Kraska, A. Talwalkar, J. C. Duchi, R. Griffith, M. J.
Franklin, and M. I. Jordan. MLbase: A distributed machine-learning system. In \textit{Proc. Conf. on Innovative Data Systems Research (CIDR), 2013}.

\bibitem{golub}
G. Golub and C. E. Reinsch. Singular value decomposition and least squares solutions. \textit{Numerische Mathematik}, 14(5), 1970.

\bibitem{demmel}
J. Demmel and W. Kahan. Accurate singular values of bidiagonal matrices. \textit{SIAM J. Sci. Stat. Comput}, 11(5), 1990.

\bibitem{roman}
V. Hernandez, J. Roman, and A. Tomas. A robust and efficient parallel SVD solver based on restarted Lanczos bidiagonalization. \textit{Electronic Transactions on Numerical Analysis}, 31, 2008.

\bibitem{halko}
N. P. Halko. Randomized methods for computing low-rank approximations of matrices. \textit{PhD thesis, University of Colorado}, 2012.

\bibitem{bishop}
M. E. Tipping and C. M. Bishop. \textit{Mixtures of probabilistic principal component analysers}. \textit{Neural Computation, 11(2)}, 1999.

\bibitem{nokia}
Nokia White Paper. \textit{Datacenter interconnect market trends and requirements}.
weblink: \texttt{\url{https://resources.ext.nokia.com/?cid=181666}}

\bibitem{fujitsu}
Fujitsu White Paper. \textit{Application Note: Data Center Interconnect}.
weblink: \texttt{\url{http://www.fujitsu.com/us/Images/Data-Center-Interconnect-app-note.pdf}}

\bibitem{spark}
M. Zaharia, M. Chowdhury, T. Das, A. Dave, J. Ma,
M. McCauley, M. J. Franklin, S. Shenker, and I. Stoica. Resilient distributed datasets: A fault-tolerant abstraction for in-memory cluster computing. In Proc. \textit{USENIX Conf. on Networked Systems Design and Implementation (NSDI)}, NSDI’12. USENIX Association, 2012.

\bibitem{spark-site}
Tutorials Point Tutorial. weblink: \texttt{\url{https://www.tutorialspoint.com/apache_spark/apache_spark_rdd.htm}}
\end{thebibliography}

\endinput